A Detection of the Environmental Dependence of the Sizes and Stellar Haloes of Massive Central Galaxies

### 2017-08-08 draft/paper2_v5.tex
Response to Jenny's comments

% Version 0; preprint format; Outline of paper II by Song Huang
% Version 1; preprint format; Edited by Jenny Greene
% Version 2; preprint format; Edited by Song Huang
% Version 3; preprint format; Edited by Alexie Leauthaud

@@

    We use ${\sim}100$ deg$^2$ of deep ($>28.5$\sb{} in $i$-band), high-quality 
    (median 0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
    to investigate the halo mass dependence of the surface mass density profiles 
    and outer stellar envelopes of massive galaxies. 
    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
    enables us to directly trace stellar mass distributions to 100 kpc without 
    requiring stacking.  
    We conclusively show that at fixed stellar mass, the stellar profiles of massive 
    galaxies depend on the masses of the their dark matter halos. 
    On average, massive central galaxies in more massive halos have shallower inner 
    stellar mass density profiles (within ${\sim}10$-$20$ kpc) and more prominent 
    outer envelopes. 
    These differences translate into a clear environmental dependence of the 
    mass-size relation: central galaxies in more massive halos have larger 
    $R_{\mathrm{50}}$ at fixed \mtot{}.  
    Our results are broadly consistent with the two phase formation scenario of 
    massive galaxies in which outer envelopes are built up at late times from the 
    accretion of small systems.

@@

    There have been multiple observational attempts to test the two-phase 
    formation scenario using galaxies at low redshift, by investigating surface 
    brightness or mass density profiles (e.g. \citealt{Huang2013a, Huang2013b, 
    Oh2017}, optical color gradients (e.g. \citealt{LaBarbera2010, LaBarbera2012}), 
    and stellar population gradients \citep[e.g.,][]{Coccato2010, Coccato2011, 
    Greene2015, Barbosa2016}. 
    Although these observations are generally consistent with the two-phase scenario, 
    this picture still faces a key puzzle: whether or not sizes and profiles of galaxies 
    depend on their mass of their host dark matter halos.

@@

   We use these two simple metric masses to explore the \mstar{}-dependence of the 
   fraction of accreted stars, and reveal to the diversity of stellar envelopes among 
   massive galaxies. 
   In practice, we also have the full profiles for each galaxy and can also cast our 
   results in terms of the full stellar mass profiles. 
   However, in many cases we find it more useful to display figures using the more 
   simple \minn{} and \mtot{} quantities. 
   In Figure \ref{fig:m100_m10_color}, we highlight the diversity of galaxies as a 
   function of \minn{} and \mtot{}. 
   Figure \ref{fig:m100_m10_color} shows a random subsample of massive galaxies with 
   very similar \minn{} that have large range of \mtot{}. 
   We will use these two apertures masses to guide our comparisons of massive galaxies 
   as a function of environments.

@@

    Firstly, we select 68 massive central galaxies from \redm{} clusters 
    with $\lambda \geq 30$, $P_{\mathrm{Cen}} \geq 0.7$, and \logmtot{}$>11.5$ 
    at $0.3 < z < 0.5$ (63/68 have \logmtot{}$>11.6$). 
    This $\lambda$ limit is chosen to mitigate incompleteness in the cluster catalog
    at the high end of our redshift window. 
    The $P_{\mathrm{Cen}}$ limit is selected to exclude low probability candidate of 
    central galaxy. 
    Based on the \mhalo{}-$\lambda$ relation calibrated by \citet{Simet2016}, these 
    correspond to central galaxies living in halos with \mhalo{}$>10^{14.2}$~\msun{}. 
    This calibration is consistent with other works (e.g. \citealt{Saro2015, Farahi2016, 
    Melchior2016, Murata2017}). 
    The median richness of the sample is $\lambda \approx 41$ 
    (\mhalo{}$\approx 2.2 \times 10^{14}$~\msun{}), and there are 
    only 44 central galaxies in clusters with $\lambda>50$ 
    (\mhalo{}$\approx 3.0 \times 10^{14}$~\msun{}).
    We will refer to this sample of \textbf{central galaxies in massive haloes} as 
    the \rbcg{} sample.

@@

    We note that our method fails to extract 1-D profiles for $\sim10$\% of 
    \rbcg{} and \nbcg{} galaxies due on-going major mergers or projection effects 
    (e.g.\ nearby foreground galaxy or bright stars). 
    However, this small failure rate should not affect any of the results in this paper.

@@

%% ------------------------------------------------------------------------------------ %% 
\subsection{Environmental Dependence of the Profiles of Massive Galaxies}
    \label{ssec:sbp_mtot}

    First, we ask whether the \mden{} profiles of massive central galaxies depend on 
    halo mass at fixed stellar mass. 
    To ask this question, however, we must first define which stellar mass exactly is 
    being fixed in the comparison. 
    We will show comparisons of \mden{} profiles at both fixed \mtot{} as well as fixed 
    \minn{}. 
    We also ensure that all comparisons are performed with fixed underlying redshift
    distribution by matching samples in redshift in addition to stellar mass
    (please see Appendix~\ref{app:match}, Appendix~\ref{app:redshift}, 
    and Fig~\ref{fig:match} for details).

@@

%% ------------------------------------------------------------------------------------ %%     
    Fig~\ref{fig:prof_1} compares the \mden{} profiles of massive central galaxies 
    living in less massive dark matter haloes (\logmh$<14.0$) to those living in more 
    massive dark matter haloes (\logmh$>14.2$) at fixed \mtot{} (left panel) and at 
    fixed \minn{} (right panel). 
    This figure shows the main result of this paper, namely that 
    \textbf{the \mden{} profiles of massive central galaxies show a clear dependence on 
    dark matter halo mass at both fixed \mtot{} and \minn{}.}

@@

        \item For the \mtot{} matched sample, although there is a clear and robust 
            difference between the two median \mden{} profiles, the overall difference 
            is quite subtle, especially in the inner region. 
            The difference becomes more apparent at $R>50$ kpc scales.

        \item At fixed \mtot{}, central galaxies in more massive dark matter haloes 
            display shallower \mden{} profiles compared to those living in low mass 
            dark matter haloes (they have a flatter inner \mden{} profiles and 
            more significant outer stellar haloes.

        \item The median \mden{} profiles of the \rbcg{} and \nbcg{} samples cross 
            each other at ${\sim} 15$-20 kpc, roughly the typical effective radius 
            ($R_{\mathrm{e}}$) of massive galaxies with \logmtot{}$>11.7$--11.8.

        \item Finally, the differences between the two sets of profiles becomes 
            more prominent at higher \mtot{}. 
            This can be seen further dividing the sample into two \mtot{} bins 
            (see Fig~\ref{fig:prof_2} and discussion in Appendix~\ref{app:robust}) 
            and when we discuss the relation between \mtot{} and 
            \minn{} (see Fig~\ref{fig:scaling_relation}). 
            This trend potentially indicates that the assembly of stellar haloes in 
            more massive central galaxies become more sensitive to their 
            environments or halo mass.

@@

    The logarithmic scale of \mden{} on the Y-axis is partially responsible for the 
    subtle differences we see in the fixed \mtot{} comparison.  
    In Appendix \ref{app:cog} and Figure~\ref{fig:cog}, we present the same 
    comparison using the curve--of--growth of \mstar{} and the fraction of \mtot{} 
    enclosed in elliptical apertures with different radius. 
    Both of the illustrate the same results from slightly different angles. 
    They also both suggest that, at fixed \mtot{}, the environmental dependence of 
    \mden{} profiles is indeed quite subtle. 
    This may explain why previous attempts to detect such dependence using shallower 
    images often failed. 
    More importantly, this result also suggests that halo mass does not play the 
    central role in shaping massive central galaxies \textbf{at fixed ``total'' 
    stellar mass}.

    It is therefore interesting to see the comparison of \mden{} profiles at fixed 
    \minn{}--a reasonable tracer for the stellar mass in the \textit{in situ}
    component (right panel of Fig~\ref{fig:prof_1}).  
    Although the median \mden{} profiles are very similar at $R \leq 10$ kpc, the
    massive central galaxies in more massive haloes host much more prominent outer 
    stellar halo. 
    Also, the similar slopes of the \mden{} profiles within 10 kpc are in sharp 
    contrast with the large \textit{intrinsic} scatter we see in the outer \mden{} 
    profiles. 
    This hints that these two regions could be shaped by distinctive physical 
    processes, and may explain why they depend on halo mass differently.  
    In simulations, intensive dissipative process helps create 
    self-similar de~Vaucouleur-like ($n{\sim} 4$) \mden{} profile in the inner part 
    of massive galaxy (e.g. \citealt{Hopkins2008}), and the \mhalo{}-dependent
    merging history leads to shallower stellar halo profile for central galaxy 
    of more massive halo (e.g. \citealt{Pillepich2014}). 
    The scatter of halo assembly histories at fixed halo mass and the stochastic 
    nature of the galaxy--galaxy mergers also explain the large \textit{intrinsic} 
    scatter in the outer \mden{} profiles and the diversity seen on the 
    \mtot{}--\minn{} plane (Fig~\ref{fig:m100_m10_color}).

    \textbf{In summary, we reliably detect subtle, but systematic \mhalo{}-dependence 
    (environmental dependence) of \mden{} profiles within 100 kpc in massive central 
    galaxies}. 
    Such dependence seems to be consistent with the expectation of more (minor) 
    mergers in more massive dark matter haloes. 
    Non-dissipative (minor) mergers should not strongly alter the inner \mden{} 
    profiles, but can build up the outer halo efficiently
    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013}).

@@

    The previous section clearly showed that the \mden{} profiles of massive central 
    galaxies depend on the masses of their host dark matter halos. 
    We now ask whether or not this dependence is also manifest when considered in 
    terms of the more traditionally studied \mstar{}--$R_{\mathrm{e}}$ relation. 
    However, when considering the mass-size relation, there is ambiguity and there are
    multiple approaches to define ``sizes''. 
    This is especially relevant in the context of massive galaxies with extended 
    stellar haloes (a reason why we prefer to show \mden{} profiles directly as in 
    the previous section). 
    In this section, we still use \mtot{} as proxy of ``total'' \mstar{} and we adopt 
    the radius enclosing 50\% of stellar mass within 100 kpc ($R_{\mathrm{50}}$; 
    derived from the $i$-band curve-of-growth) as the ``size''. 
    This definition of ``effective radius'' is more robust against structural details, 
    choice of model, and the background subtraction comparing to the effective radius 
    estimated by simple 2-D modeling method (e.g. single-\ser{} model). 
    Massive galaxies from this sample are large enough that the impact of seeing is 
    not a concern.

@@

    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, galaxies 
    in more and less massive dark matter haloes lie on \mtot{}--$R_{\mathrm{50}}$ 
    relations that have similar slopes but different normalizations. 
    This result is robust against the ranges of \mstar{} over which the fit is performed 
    and against the definitions of  ``total'' \mstar{} and half-light 
    radius\footnote{Using \mstar{} within 120 or 150 kpc, or using the 
    $R_{\mathrm{50}}$ derived within these apertures do not change the results.}.

    We qualitatively compare our results with \citealt{HCompany13} (HC13; 
    green solid line) who studied $z\leq 0.09$ central ETGs in 
    $12.5 \le$ \logmh{} $< 15$ haloes. 
    HC13 use the group catalog by \citet{Yang2007} to estimate halo mass. 
    They obtain effective radii from single-\ser{} model fitting to SDSS 
    images and \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
    synthetic population model. 
    We convert their \mstar{} estimates from a Kroupa IMF to a Chabrier 
    IMF by applying a constant -0.05 dex shift (see \citealt{Bernardi2016a}). 
    We further add $+0.1$dex to the HSC13 stellar masses to account for a systematic 
    offset between BC03 and our FSPS model (see Paper~1). 
    The distributions of galaxies on the 
    \mtot{}--$R_{\mathrm{50}}$ plane follow the HC13 relation reasonably well 
    (with slightly shallower slopes), even at \logmtot{}$< 11.6$ where our samples 
    start to become incomplete in stellar mass. 
    In contrast to the present study, HC13 finds no environment dependence in the 
    mass--size relation for central galaxies in the range $12.5\le$ \logmh{} $<15.0$.     
    However, HC13 use SDSS images that are considerably shallower compared to the HSC 
    ones and hence will not be as sensitive to the outer portions of the \mden{} 
    profile where we see the most clear differences. 
    A more detailed comparison is beyond the scope of this work, but in 
    Appendix~\ref{app:gama}, we use the \rbcg{} and \nbcg{} galaxies that overlap 
    with the GAMA survey to briefly demonstrate this point. 
    We show that, for galaxies with similar \mstar{} derived from single-\ser{} 
    models using shallower SDSS images (\citealt{Kelvin2012}), the ones in more 
    massive dark matter halos actually show more prominent outer stellar halos, 
    hence both of their stellar mass and effective radius are underestimated.  
    This shows again that the deeper HSC images has unique advantage in studying the
    connection between the assembly of massive galaxies and their dark matter haloes.

@@

    From Figure \ref{fig:scaling_relation} we can draw the same conclusions as in 
    the previous section, namely that: 
    at fixed \mtot{}, central galaxies in more massive haloes tend to have smaller 
    fraction of stellar mass in their inner regions and higher \mstar{} in their outer
    stellar haloes. 
    Although the HSC images can not resolve the central region of these massive 
    galaxies, the on average lower \mstar{} within 10 kpc and shallower inner \mden{} 
    profile for massive central galaxies living in more massive haloes are robust 
    results and could have interesting physical implications.
    Meanwhile, at fixed \minn{}--a proxy for the \mstar{} of the ``in situ'' component,
    central galaxies in more massive haloes tend to be more massive and display more 
    prominent stellar haloes. 
    The scientific implication of these results will be discussed in 
    Section~\ref{sec:discussion}.

@@

    \begin{itemize}
        \item Within $R>50$ kpc, we find that the ellipticity profiles of massive 
            central galaxies do not depend on halo mass at fixed \mtot{}.

@@

    Besides these conclusions, the fact that we find smooth ellipticity profile and 
    its shallow gradient favors the idea of using the flux-weighted average isophotal 
    shape to extract 1-D \mden{} profiles of massive galaxies. 
    The similarity of average rest-frame color profiles between the \rbcg{} and \nbcg{}
    samples suggests that \mden{} profiles based on single average \m2l{} will not bias 
    our comparisons.

@@

    \citet{Shankar2014} studied the environment dependence of galaxy size using 
    a series of hierarchical semi-analytic models. 
    They predict that at fixed stellar mass, the median size of central galaxies 
    should increase strongly with halo mass. 
    The major-merger rate only increases slightly with halo mass (mass ratio $>1$:3; 
    e.g. \citealt{Hirschmann2013}). 
    The minor-merger rate, however, depends strongly on the dynamical friction time. 
    If the dynamical friction time is short (e.g. \citealt{Newman2012}), the
    massive central galaxies with $11.5 <$\logms{}$<12.0$ from more massive haloes 
    (\logmh{}$>14.0$) can have up to four times more minor mergers (1:100--1:3)
    comparing to the ones in less massive halos at similar stellar mass. 
    This increase in the minor-merger rate as a function of halo mass leads to a 
    halo-mass dependence in the mass-size relation. 
    The prediction from \citet{Shankar2014} have been confirmed by \citet{Yoon2017} 
    using the semi-analytic model from \citet{Guo2011}.  
    Our results are broadly consistent with these predictions. 
    Indeed, we find that the outer profiles of massive galaxies ($r>50$ kpc) are the 
    regions that display the strongest variations as a function of halo mass.

@@

    At the same time, from the comparison of median \mden{} profiles of the 
    \mtot{}--matched samples and from the \mtot{}--\minn{} plane, our results also 
    show that the centrals of more massive haloes have slightly shallower inner 
    \mden{} slope and lower fraction of \mtot{} within the inner 10 kpc.
    It seems that the environmental dependence of stellar mass distributions in 
    massive central galaxies also affects their central region.
    Unlike the differences in the outer stellar halo, it is difficult to use minor 
    mergers to explain such difference as they should not alter the inner \mden{} 
    profiles. 
    It is also not caused by the choice of outer aperture to estimate ``total''
    \mstar{}: assuming that centrals in more massive haloes have more extended 
    \mden{} profiles, integration out to larger aperture will make the differences 
    between \rbcg{} and \nbcg{} galaxies on the \mtot{}--\minn{} plane more 
    significant.

    Several physicals processes may help shape the stellar mass distributions in the 
    inner region. 
    For instance, strong adiabatic expansion induced by powerful AGN feedback can 
    lead to more flattened inner \mden{} profile \citealt{Fan2008}. 
    The violent relaxation process involved in the major dry merger can reshape 
    stellar mass distributions in the inner region. 
    In addition, the coalesce of super-massive black hoes (SMBHs) at the end of 
    major merger, which is common in the assembly history of massive galaxies, can 
    also flatten the central \mden{} profile via efficient scattering effect 
    (e.g. \citealt{Milosavljevi2002}).
    On the right side of Fig \ref{fig:scaling_relation}, we find a few \rbcg{} 
    galaxies with very low \minn{} at high \mtot{} end that are apparently not bothered 
    by problematic photometry or exceptionally bad seeing.  
    They may be similar to the recently discovered massive BCGs with very large 
    depleted cores (a few kpc; e.g. \citealt{Postman2012, LopezCruz2014, Thomas2016,
    Bonfini2016}) resulting from SMBH mergers.
    The impacts of these processes, and their dependence on \mhalo{} is an interesting 
    topic to investigate in the future through comparisons with both observations 
    at high redshift and numerical simulations.

>>>>

% Version 0; preprint format; Outline of paper II by Song Huang
% Version 1; preprint format; Edited by Jenny Greene
% Version 2; preprint format; Edited by Song Huang
% Version 3; preprint format; Edited by Alexie Leauthaud
% Version 4; preprint format; Edited by Song Huang
% Version 5; preprint format; Edited by Jenny Greene and Song Huang

@@

    We use ${\sim}100$ deg$^2$ of deep ($>28.5$\sb{} in $i$-band), high-quality 
    (median 0.6\asec seeing) imaging data from the Hyper Suprime-Cam (HSC) survey 
    to investigate the halo mass dependence of the surface mass density profiles 
    and outer stellar envelopes of massive galaxies. 
    The depth of the HSC survey reaches ${\sim}4$ magnitudes fainter than SDSS and 
    enables us to directly trace stellar mass distributions to 100 kpc without 
    requiring stacking.  
    We conclusively show that at fixed stellar mass, the stellar profiles of massive 
    galaxies depend on the masses of their dark matter halos. 
    On average, massive central galaxies in more massive halos have shallower inner 
    stellar mass density profiles (within ${\sim}10$-$20$ kpc) and more prominent 
    outer envelopes. 
    These differences translate into a clear environmental dependence of the 
    mass-size relation: central galaxies in more massive halos have larger 
    $R_{\mathrm{50}}$ at fixed \mtot{}.  
    Our results are broadly consistent with the two phase formation scenario of 
    massive galaxies in which outer envelopes are built up at late times from the 
    accretion of small systems.

@@

    There have been multiple observational attempts to test the two-phase 
    formation scenario using galaxies at low redshift, by investigating surface 
    brightness or mass density profiles (e.g. \citealt{Huang2013a, Huang2013b, 
    Oh2017}, optical color gradients (e.g. \citealt{LaBarbera2010, LaBarbera2012}), 
    and stellar population gradients \citep[e.g.,][]{Coccato2010, Coccato2011, 
    Greene2015, Barbosa2016}. 
    Although these observations are generally consistent with the two-phase scenario, 
    this picture still faces a key puzzle: whether or not sizes and profiles of galaxies 
    depend on the mass of their host dark matter halos.

@@

   We use these two simple metric masses to explore the \mstar{}-dependence of the 
   fraction of accreted stars, and reveal the diversity of stellar envelopes among 
   massive galaxies. 
   In practice, we also have the full profiles for each galaxy and can cast our 
   results in terms of the full stellar mass profiles. 
   However, in many cases we find it more useful to display figures using the more 
   simple \minn{} and \mtot{} quantities. 
   In Figure \ref{fig:m100_m10_color}, we highlight the diversity of galaxies as a 
   function of \minn{} and \mtot{}. 
   Figure \ref{fig:m100_m10_color} shows a random subsample of massive galaxies with 
   very similar \minn{} that have large range of \mtot{}. 
   We will use these two apertures masses to guide our comparisons of massive galaxies 
   as a function of environment.

@@

    Firstly, we select 68 massive central galaxies from \redm{} clusters 
    with richness ($\lambda$) $\geq 30$, and the probability of true central galaxy 
    ($P_{\mathrm{Cen}}$) $\geq 0.7$, and \logmtot{}$>11.5$ 
    at $0.3 < z < 0.5$ (63/68 have \logmtot{}$>11.6$). 
    This $\lambda$ limit is chosen to mitigate incompleteness in the cluster catalog
    at the high end of our redshift window. 
    The $P_{\mathrm{Cen}}$ limit is selected to exclude low probability candidate of 
    central galaxy. 
    Based on the \mhalo{}-$\lambda$ relation calibrated by \citet{Simet2016}, these 
    correspond to central galaxies living in halos with \mhalo{}$>10^{14.2}$~\msun{}. 
    This calibration is consistent with other works (e.g. \citealt{Saro2015, Farahi2016, 
    Melchior2016, Murata2017}). 
    The median richness of the sample is $\lambda \approx 41$ 
    (\mhalo{}$\approx 2.2 \times 10^{14}$~\msun{}), and there are 
    only 44 central galaxies in clusters with $\lambda>50$ 
    (\mhalo{}$\approx 3.0 \times 10^{14}$~\msun{}).
    We will refer to this sample of \textbf{central galaxies in massive haloes} as 
    the \rbcg{} sample.

@@

    We note that our analysis fails to extract 1-D profiles for $\sim10$\% of 
    \rbcg{} and \nbcg{} galaxies due on-going major mergers or projection effects 
    (e.g.\ nearby foreground galaxy or bright stars). 
    However, this small failure rate should not affect any of the results in this paper.

@@

%% ------------------------------------------------------------------------------------ %% 
\subsection{Environmental Dependence of the Stellar Mass Density Profiles of Massive 
            Galaxies}
    \label{ssec:sbp_mtot}

    First, we ask whether the \mden{} profiles of massive central galaxies depend on 
    halo mass at fixed stellar mass.
    %To ask this question, however, we must first define which stellar mass exactly is 
    %being fixed in the comparison.

    We will show comparisons of \mden{} profiles at both fixed \mtot{} as well as fixed 
    \minn{}. 
    We also ensure that all comparisons are performed with fixed underlying redshift
    distribution by matching samples in redshift in addition to stellar mass
    (please see Appendix~\ref{app:match}, Appendix~\ref{app:redshift}, 
    and Fig~\ref{fig:match} for details).

@@

%% ------------------------------------------------------------------------------------ %%     
    Fig~\ref{fig:prof_1} compares the \mden{} profiles of massive central galaxies 
    living in less massive dark matter haloes (\logmh$<14.0$) to those living in more 
    massive dark matter haloes (\logmh$>14.2$) at fixed \mtot{} (left panel) and at 
    fixed \minn{} (right panel). 
    At fixed \mtot{}, we compare massive galaxies that have similar ``total'' \mstar{}. 
    On the right side, we use \minn{} as proxy of the \textit{in situ} \mstar{} to 
    compare the overall \mstar{} distributions of galaxies living in different 
    environments that have assembled similar amount of stars at high-$z$.
    This figure shows the main result of this paper, namely that 
    \emph{the \mden{} profiles of massive central galaxies show a clear dependence on 
    dark matter halo mass at both fixed \mtot{} and \minn{}.}

@@

        \item For the \mtot{}--matched samples, although there is a clear and robust 
            difference between the two median \mden{} profiles, the overall difference 
            is quite subtle, especially in the inner region. 
            The difference becomes more apparent at $R>50$ kpc scales.

        \item At fixed \mtot{}, central galaxies in more massive dark matter haloes 
            display shallower \mden{} profiles compared to those living in low mass 
            dark matter haloes (they have a flatter inner \mden{} profiles and 
            more significant outer stellar haloes. 
            The median \mden{} profiles of the \rbcg{} and \nbcg{} samples cross 
            each other at ${\sim} 15$-20 kpc, roughly the typical effective radius 
            ($R_{\mathrm{e}}$) of massive galaxies with \logmtot{}$>11.7$--11.8.

        \item For the \minn{}--matched samples, their median \mden{} profiles 
            are very similar at $R \leq 10$ kpc. 
            However, massive galaxies with similar \mstar{} within 10 kpc have quite
            different \mtot{}, and the massive central galaxies in 
            more massive haloes host much more prominent outer stellar halo.

        \item Also, for the \minn{}--matched samples, the similar slopes of the 
            \mden{} profiles within 10 kpc are in sharp contrast with the large
            \textit{intrinsic} scatter we see in the outer \mden{} profiles.

@@

    The logarithmic scale of \mden{} on the Y-axis is partially responsible for the 
    subtle differences we see in the fixed \mtot{} comparison.  
    In Appendix \ref{app:cog} and Figure~\ref{fig:cog}, we present the same 
    comparison using the curve--of--growth of \mstar{} and the fraction of \mtot{} 
    enclosed in elliptical apertures with different radius. 
    Both of the illustrate the same results from slightly different angles. 
    They also both suggest that, at fixed \mtot{}, the environmental dependence of 
    \mden{} profiles is indeed quite subtle. 
    This may explain why previous attempts to detect such dependence using shallower 
    images often failed. 
    More importantly, this result also suggests that halo mass does not play the 
    central role in shaping massive central galaxies \textbf{at fixed ``total'' 
    stellar mass}.
    Also, the differences in median \mden{} profiles seem to become more prominent 
    at higher \mtot{}. 
    This is demonstrated in Appendix~\ref{app:robust} (see Fig~\ref{fig:prof_2}). 
    Although this trend still needs to be confirmed by larger samples, it 
    potentially indicates that the assembly of stellar haloes in more massive 
    central galaxies become more sensitive to their environments.

    Meanwhile, the comparison of \mden{} profiles at fixed \minn{}--a reasonable 
    tracer for the stellar mass in the \textit{in situ} component (right panel of 
    Fig~\ref{fig:prof_1}) hints that the inner region ($<10$ kpc) and the outer 
    stellar halo could be shaped by distinctive physical processes, and may explain 
    why they depend on halo mass differently.  
    In simulations, intensive dissipative process helps create 
    self-similar de~Vaucouleur-like ($n{\sim} 4$) \mden{} profile in the inner part 
    of massive galaxy (e.g. \citealt{Hopkins2008}), and the \mhalo{}-dependent
    merging history leads to shallower stellar halo profile for central galaxy 
    of more massive halo (e.g. \citealt{Pillepich2014}). 
    The scatter of halo assembly histories at fixed halo mass and the stochastic 
    nature of the galaxy--galaxy mergers also explain the large \textit{intrinsic} 
    scatter in the outer \mden{} profiles and the diversity seen on the 
    \mtot{}--\minn{} plane (Fig~\ref{fig:m100_m10_color}).

    \textbf{In summary, we reliably detect subtle, but systematic \mhalo{}-dependence 
    (environmental dependence) of \mden{} profiles within 100 kpc in massive central 
    galaxies. 
    Such dependence seems to be consistent with the expectation of more (minor) 
    mergers in more massive dark matter haloes. 
    Non-dissipative (minor) mergers should not strongly alter the inner \mden{} 
    profiles, but can build up the outer halo efficiently
    (e.g. \citealt{Hilz2013}, \citealt{Oogi2013})}.

@@

    The previous section clearly showed that the \mden{} profiles of massive central 
    galaxies depend on the masses of their host dark matter halos. 
    We now ask whether or not this dependence is also manifest when considered in 
    terms of the more traditionally studied \mstar{}--$R_{\mathrm{e}}$ relation. 
    However, when considering the mass-size relation, there is ambiguity and there are
    multiple approaches to define ``sizes''. 
    This is especially relevant in the context of massive galaxies with extended 
    stellar haloes (a reason why we prefer to show \mden{} profiles directly as in 
    the previous section). 
    In this section, we still use \mtot{} as proxy of ``total'' \mstar{} and we adopt 
    the radius enclosing 50\% of stellar mass within 100 kpc ($R_{\mathrm{50}}$; 
    derived from the $i$-band curve-of-growth) as the ``size''. 
    This definition of ``effective radius'' is more robust against structural details, 
    choice of model, and the background subtraction compared to the effective radius 
    estimated by simple 2-D modeling method (e.g. single-\ser{} model). 
    Massive galaxies from this sample are large enough that the impact of seeing is 
    not a concern.

@@

    \noindent As shown in the left panel of Fig~\ref{fig:scaling_relation}, 
    galaxies in more and less massive dark matter haloes lie on 
    \mtot{}--$R_{\mathrm{50}}$ relations that have similar slopes but 
    different normalizations. 
    The best-fit mass--size relations derived here suggests that, 
    at $0.3 < z < 0.5$, central galaxies with \logmtot{}$>11.6$ in \logmhalo{}$>14.0$
    haloes are on average $\sim20$\% larger than the centrals from \logmhalo{}$<14.0$
    haloes at fixed \mtot{}.
    This result is robust against the ranges of \mstar{} over which the fit is 
    performed and against the definitions of  ``total'' \mstar{} and half-light 
    radius\footnote{Using \mstar{} within 120 or 150 kpc, or using the 
    $R_{\mathrm{50}}$ derived within these apertures do not change the results.}. 
    Given the uncertainties of the best-fit parameters, the differences in 
    mass--size relation is not very significant.  
    It relates to the relative small sample sizes, uncertainties in \mstar{} and 
    \mhalo{} estimates, and the limited \mtot{} range used in the fitting.

    We qualitatively compare our results with \citealt{HCompany13} (HC13; 
    green solid line) who studied $z\leq 0.09$ central ETGs in 
    $12.5 \le$ \logmh{} $< 15$ haloes. 
    HC13 use the group catalog by \citet{Yang2007} to estimate halo mass. 
    They obtain effective radii from single-\ser{} model fitting to SDSS 
    images and \mstar{} based on SED fitting using the BC03 (\citealt{BC03}) 
    synthetic population model. 
    We convert their \mstar{} estimates from a Kroupa IMF to a Chabrier 
    IMF by applying a constant -0.05 dex shift (see \citealt{Bernardi2016a}). 
    We further add $+0.1$dex to the HSC13 stellar masses to account for a systematic 
    offset between BC03 and our FSPS model (see Paper~1). 
    The distributions of galaxies on the 
    \mtot{}--$R_{\mathrm{50}}$ plane follow the HC13 relation reasonably well 
    (with slightly shallower slopes), even at \logmtot{}$< 11.6$ where our samples 
    start to become incomplete in stellar mass. 
    In contrast to the present study, HC13 finds no environment dependence in the 
    mass--size relation for central galaxies in the range $12.5\le$ \logmh{} $<15.0$.     
    Both the considerably shallower SDSS images and the single-\ser{} model could 
    contribute to this difference, since the most clear environmental differences 
    are found in the low surface brightness stellar halos that can not be 
    well-modeled with the inner portion of the \mden{} profile using single-\ser{}
    profiles.

@@

    From Figure \ref{fig:scaling_relation} we can draw the same conclusions as in 
    the previous section, namely that: 
    at fixed \mtot{}, central galaxies in more massive haloes tend to have smaller 
    fraction of stellar mass in their inner regions and higher \mstar{} in their outer
    stellar haloes. 
    Meanwhile, at fixed \minn{}--a proxy for the \mstar{} of the ``in situ'' component,
    central galaxies in more massive haloes tend to be more massive and display more 
    prominent stellar haloes. 
    The scientific implication of these results will be discussed in 
    Section~\ref{sec:discussion}.

    % Although the HSC images can not resolve the central region of these massive 
    % galaxies, the on average lower \mstar{} within 10 kpc and shallower inner \mden{} 
    % profile for massive central galaxies living in more massive haloes are robust 
    % results and could have interesting physical implications.

@@

    \begin{itemize}
        \item Within $R<50$ kpc, we find that the ellipticity profiles of massive 
            central galaxies do not depend on halo mass at fixed \mtot{}.

@@

    Besides these conclusions, the fact that we find smooth ellipticity profiles and 
    shallow gradients favors the idea of using the flux-weighted average isophotal 
    shape to extract 1-D \mden{} profiles of massive galaxies. 
    The similarity of average rest-frame color profiles between the \rbcg{} and \nbcg{}
    samples suggests that \mden{} profiles based on single average \m2l{} will not bias 
    our comparisons.

@@

    \citet{Shankar2014} studied the environment dependence of galaxy size using 
    a series of hierarchical semi-analytic models. 
    They predict that at fixed stellar mass, the median size of central galaxies 
    should increase strongly with halo mass. 
    The major-merger rate only increases slightly with halo mass (mass ratio $>1$:3; 
    e.g. \citealt{Hirschmann2013}). 
    The minor-merger rate, however, depends strongly on the dynamical friction time. 
    If the dynamical friction time is short (e.g. \citealt{Newman2012}), the
    massive central galaxies with $11.5 <$\logms{}$<12.0$ from more massive haloes 
    (\logmh{}$>14.0$) can have up to four times more minor mergers (1:100--1:3)
    compared to the ones in less massive halos at similar stellar mass. 
    This increase in the minor-merger rate as a function of halo mass leads to a 
    halo-mass dependence in the mass-size relation. 
    The predictions from \citet{Shankar2014} have been confirmed by \citet{Yoon2017} 
    using the semi-analytic model from \citet{Guo2011}.  
    Our results are broadly consistent with these predictions. 
    Indeed, we find that the outer profiles of massive galaxies ($r>50$ kpc) are the 
    regions that display the strongest variations as a function of halo mass.

@@

    At the same time, from the comparison of median \mden{} profiles of the 
    \mtot{}--matched samples and from the \mtot{}--\minn{} plane, our results also 
    show that the centrals of more massive haloes have slightly shallower inner 
    \mden{} slope and lower fraction of \mtot{} within the inner 10 kpc.
    It seems that the environmental dependence of stellar mass distributions in 
    massive central galaxies also affects their central region.
    This is not caused by the choice of outer aperture to estimate ``total''
    \mstar{}: assuming that centrals in more massive haloes have more extended 
    \mden{} profiles, integration out to larger aperture will make the differences 
    between \rbcg{} and \nbcg{} galaxies on the \mtot{}--\minn{} plane more 
    significant.

    Several physicals processes may help shape the stellar mass distributions in the 
    inner region. 
    Major merger can redistribute the inner stellar mass distributions, but major
    merger rate does not strongly depend on halo mass. 
    Although recent simulations tend to emphasize the contribution of dry minor 
    mergers in building up the outer envelope, simulation also shows that minor 
    mergers can modify the central surface brightness profiles of the remnants
    (e.g. \citealt{BoylanKolchin2007}). 
    Depending on the structure and infalling orbit of the satellite, minor merger 
    can make the inner \mden{} profiles both flattened or steepened.  
    Interestingly, these authors find, when satellite is accreted from a highly 
    eccentric and energetic orbit to a core--elliptical galaxy, it tends to reduce 
    the central \mden{}.  
    This is relevant here as many massive BCGs are known to be core--elliptical 
    galaxies. 
    Also, strong adiabatic expansion induced by powerful AGN feedback can be another 
    interesting option (e.g. \citealt{Fan2008}). 
    This proposed efficient mass--loss can expand the central stellar mass 
    distribution low central \mden{}.  
    In addition, at smaller scale, the coalesce of super-massive black hoes (SMBHs)  
    can flatten the central \mden{} profile via efficient scattering effect 
    (e.g. \citealt{Milosavljevi2002}).
    On the right side of Fig \ref{fig:scaling_relation}, we find a few \rbcg{} 
    galaxies with very low \minn{} at high \mtot{} end that are apparently not bothered 
    by problematic photometry or exceptionally bad seeing.  
    They may be similar to the recently discovered massive BCGs with very large 
    depleted cores (a few kpc; e.g. \citealt{Postman2012, LopezCruz2014, Thomas2016,
    Bonfini2016}) resulting from SMBH mergers.
    The impacts of these processes, and their dependence on \mhalo{} is an interesting 
    topic to investigate in the future through comparisons with both observations 
    at high redshift and numerical simulations.
